2.4: OLS: Goodness of Fit and Bias

### 2019-10-01 static/slides/10-slides.Rmd
Add class 11 content

2. The variance of the residuals is constant, written:
$$var(u)=\sigma^2_{u}$$

@@

# Assumption 2: Heteroskedasticity

@@

- The variance of the residuals is constant, written:
$$var(u)=\sigma^2_{u}$$

- Assumption 2 implies that errors are ".shout[homoskedastic]:
 they have the same variance across $X$

- Often this assumption is violated: errors may be ".shout[heteroskedastic]:
 they do not have the same variance across $X$

>>>>

2. The variance of the residuals over $X$ is constant, written:
$$var(u|X)=\sigma^2_{u}$$

@@

# Assumption 2: Homoskedasticity

@@

- The variance of the residuals over $X$ is constant, written:
$$var(u|X)=\sigma^2_{u}$$

- Assumption 2 implies that errors are ".shout[homoskedastic]:"
 they have the same variance across $X$

- Often this assumption is violated: errors may be ".shout[heteroskedastic]:"
 they do not have the same variance across $X$
